---
title: "DS400: Assignment V (R)"
author: "Janik Müller (Student ID: 6303477) - worked together with Christopher Forschner and Simon Andres"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  html_document:
    self_contained: true
---

```{r setup, include = F}
options(scipen=999)
```

***

### Setting up a new GitHub repository

<div class="alert alert-block alert-info">
1. Register on github.com in case you have not done this already.
</div>

<div class="alert alert-block alert-info">
2. Initialize a new public repository for this assignment on GitHub.
</div>

<div class="alert alert-block alert-info">
3. For the following exercises of this assignment, follow the standard Git workflow (i.e., pull the latest
version of the project to your local computer, then stage, commit, and push all the modifications that you
make throughout the project). Every logical programming step should be well documented on GitHub
with a meaningful commit message, so that other people (e.g., your course instructor) can follow and
understand the development history. You can do this either using Shell commands or a Git GUI of your
choice.
</div>

<div class="alert alert-block alert-info">
4.In the HTML file that you submit, include the hyperlink to the project repository (e.g., https://github.
com/yourUserName/yourProjectName)
</div>

```{r}

git_repository_url <- "https://github.com/Janik298/DS400-Assignment_V-.git"


```

***

### Preparing the environment


Before starting with this exercise we are loading all necessary packages into our environment. 

```{r, warning = FALSE, message = FALSE}
# Loading the packages
library(jsonlite)
library(httr)
library(tidyverse)
library(rlist)
```
***


### Getting to know the API

<div class="alert alert-block alert-info">
5.Visit the documentation website for the API provided by ticketmaster.com (see here). Familiarize yourself with the features and functionalities of the Ticketmaster Discovery API. Have a particular look at
rate limits.
</div>

Features of the API:
- The default quota is 5000 API calls per day and rate limitation of 5 requests per second.
- Deep Paging: we only support retrieving the 1000th item. i.e. ( size * page < 1000)
- Root URL: https://app.ticketmaster.com/discovery/v2/
- Event Search is possible via latitude and longitude with "latlong" - however they say one should you "geoPoint" instead 
- Overall a lot of information is provided by the API


<div class="alert alert-block alert-info">
6. Whithin the scope of this assignment, you do not have to request your own API key. Instead retrieve
a valid key from the API Explorer. This API key enables you to perform the GET requests needed
throughout this assignment. Even though this API key is not secret per se (it is publicly visible on the
API Explorer website), please comply to the common secrecy practices discussed in the lecture and the
tutorial: Treat the API key as a secret token. Your API key should neither appear in the code that you
are submitting nor in your public GitHub repository.
</div>

```{r}
source('api_key.R')
```


***

### Interacting with the API - the basics


<div class="alert alert-block alert-info">
7.Perform a first GET request, that searches for event venues in Germany (countryCode = "DE"). Extract
the content from the response object and inspect the resulting list. Describe what you can see.
</div>


```{r}
# Make a first request to get the event venues in Germany

event_venues_de <- GET("https://app.ticketmaster.com/discovery/v2/venues", 
                        query = list("apikey" = api_key,
                                "countryCode" = "DE",
                                "locale" = "*",
                                "size" = 20)) %>% content # directly extracting the contents

# With the size argument I can choose the page size of the response

```

The response is a list with three sublists. Each of those sublists contains more information. The "page" sublist contains overall information about the response. It includes infos about the number of pages, the size of those pages and the total number of available elements in the server.
The links list gives links to my current, the next and the last dataset - overall, it links to data sets. Last but not least, the _embedded list is the container and contains the information I am interested in for the analysis.


<div class="alert alert-block alert-info">
8. Extract the name, the city, the postalCode and address, as well as the url and the longitude
and latitude of the venues to a data frame. This data frame should have the following structure:
</div>

```{r}
# Extracting the wanted items
venues_de <- event_venues_de$`_embedded`$venues # this is a list containing all the venues (at least the first page)

venues_de_df <- map(.x = venues_de, as.data.frame) %>% # I now have transformed the the sublists into dataframes
                bind_rows() %>% # We now have a dataframe containing all information, but in an untidy way
                select(name, city = name.1, postal_code = postalCode, address = line1, url, longitude = location.longitude, latitude = location.latitude)
                

```

***

### Interacting with the API - advanced

<div class="alert alert-block alert-info">
9. Have a closer look at the list element named page. Did your GET request from exercise (7) return all
event locations in Germany? Obviously not - there are of course much more venues in Germany than
those contained in this list. Your GET request only yielded the first results page containing the first
20 out of several thousands of venues. Check the API documentation under the section Venue Search.
How can you request the venues from the remaining results pages? Iterate over the results pages and
perform GET requests for all venues in Germany. After each iteration, extract the seven variables name,
city, postalCode, address, url, longitude, and latitude. Join the information in one large
data frame. Print the first 10 rows and the shape of the resulting data frame. The resulting data frame
should look something like this (note that the exact number of search results may have changed since
this document has been last modified):
</div>


```{r}
# Starting with the exercise

```

***

### Visualizing the extracted data

<div class="alert alert-block alert-info">
10. Below, you can find code that produces a map of Germany. Add points to the map indicating the
locations of the event venues across Germany.
</div>



<div class="alert alert-block alert-info">
11. You will find that some coordinates lie way beyond the German borders and can be assumed to be faulty.
Set coordinate values to NA where the value of longitude is outside the range (5.866, 15.042) or
where the value of latitude is outside the range (47.270, 55.059) (these coordinate ranges have
been derived from the extreme points of Germany as listed on Wikipedia (see here). For extreme points
of other countries, see here).
</div>


***

### Event locations in other countries


<div class="alert alert-block alert-info">
12. Repeat exercises (9)–(11) for another European country of your choice. (Hint: Clean code pays off! If
you have coded the exercises efficiently, only very few adaptions need to be made.)
</div>